%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

\entrytitlestyle{Just One Marble League}
\begin{quote}
\thinspace A one-time-only league for my friends and family to celebrate and compete alongside the teams of Jelle's Marble Runs. I built this website in hopes of learning 
more about modern web development, specifically focusing on React and AWS. The backend was built with AWS Amplify for continuous deployment, a single endpoint on AWS API Gateway
that aggregated data on a simple Lambda function. Records were pulled from a DynamoDB instance that stored players' wagers as well as the marble league results.
\newline\href{https://github.com/johnsoe/thg_marbles}{\underline {Source Code}}
\end{quote}

\entrytitlestyle{Track Four}
\begin{quote}
% \\\leading{13pt}
\thinspace Infinite runner mobile game built in Godot using \href{https://docs.godotengine.org/en/stable/tutorials/scripting/gdscript/gdscript_basics.html}{\underline{GDScript}}, a python like language. Integrations with Google AdMob Launching end of February 2024.
\newline\href{https://github.com/johnsoe/Track-Four}{\underline {Source Code}}
\end{quote}

\entrytitlestyle{Advent of Code}
\begin{quote}
% \\\leading{13pt}
\thinspace Annual December coding contest where each day, two programming problems are unlocked. I have been a participant for over 5 years, and currently have 240 problems completed.
I built a tool to quickly generate necessary boilerplate code using \href{https://square.github.io/kotlinpoet/}{\underline{KotlinPoet}} and a small query to pull the content from \href{https://adventofcode.com}{\underline{Advent of Code}}
\newline\href{https://github.com/johnsoe/advent_kotlin}{\underline {My solutions (So far)}}
\end{quote}

\entrytitlestyle{Ralph and Robby}
\begin{quote}
% \\\leading{13pt}
\thinspace A website to not only learn modern web development with \href{https://kit.svelte.dev/}{\underline{SvelteKit}} but also a way to pursue my interests in making games. The 
frontend is built with Svelte and Tailwind CSS. The backend is powered by Firebase Storage, their Realtime Database, and Hosting services. 
\end{quote}



\end{cvparagraph}
